Automatic Detection of Bad Programming Habits in Scratch

### 2014-10-20 slides/slides.tex
Fix errata (median)

\begin{table}
\begin{center}
  \begin{tabular}{ | l | c | c | c |}
   \hline
              & Default names & Duplicated scripts & Defined blocks \\ \hline\hline
    Projects & 79 & 62 & 17 \\ \hline
    Mean & 5.94 & 7.23 & 1.11 \\ \hline
 22   Median & 3 & 2 & 0 \\ \hline
    Maximum & 67 & 71 & 25 \\
    \hline    
  \end{tabular}
\end{center}
\caption{Analysis of 100 ramdonly downloaded Scratch projects}
\label{table:results}
\end{table}
\end{frame}

>>>>

\begin{table}
\begin{center}
  \begin{tabular}{ | l | c | c | c |}
   \hline
              & Default names & Duplicated scripts & Defined blocks \\ \hline\hline
    Projects & 79 & 62 & 17 \\ \hline
    Mean & 5.94 & 7.23 & 1.11 \\ \hline
    Median & 3 & 2 & 0 \\ \hline
    Maximum & 67 & 71 & 25 \\
    \hline    
  \end{tabular}
\end{center}
\caption{Analysis of 100 ramdonly downloaded Scratch projects}
\label{table:results}
\end{table}
\end{frame}
